Fast, Scalable Phrase-Based SMT Decoding

### 2016-03-03 acl.2016/acl2016.tex
typo

~\newcite{Heafield-mtplz} is perhaps closest in intent to this work. This takes a holistic approach to decoding, describing a novel decoding algorithm which is focused on better decoding speed. It also describes a number of implementation details for faster decoding. However, the decoding algorithm is only able to incorporate one stateful feature function which precludes some of the useful decoding configurations which contains multiple stateful feature functions. It does not include a load-on-demand phrase table, therefore, cannot be used in a commercial environment where phrase-table has not be filtered with a know test set for any realistic size phrase-table. Neither did this paper analyze the scalability of their work to multicore servers.

>>>>

~\newcite{Heafield-mtplz} is perhaps closest in intent to this work. This takes a holistic approach to decoding, describing a novel decoding algorithm which is focused on better decoding speed. It also describes a number of implementation details for faster decoding. However, the decoding algorithm is only able to incorporate one stateful feature function which precludes some of the useful decoding configurations which contains multiple stateful feature functions. It does not include a load-on-demand phrase table, therefore, cannot be used in a commercial environment where phrase-table has not be filtered with a known test set for any realistic size phrase-table. Neither did this paper analyze the scalability of their work to multicore servers.
